SNP Analysis

### 2018-09-11 snp/SNP_Prediction_Analysis.Rmd
...

load('~/Data/Ellie/Analysis/5e6_arms_all/model_data.Rdata', verbose = T)
load('~/Data/Ellie/Analysis/5e6_arms_all/all.pt.alpha.Rdata', verbose = T)
#alpha = '0'
alpha = '0.9'
fitV = models[[alpha]]
l = performance.at.1se[[alpha]]$lambda
features = coefs[[alpha]]

@@

```{r rnormals, echo=F, warning=F, message=F, fig.width=10, fig.height=8, eval=T}
randNormal = sample(rownames(mergedSegs)[nm.rows], 1)
pt = unlist(strsplit(randNormal, '_'))[1]
segs = subset(segments.list[[pt]], chr %in% c(1:22) & grepl(sub('_', '.*', randNormal),sample))
segs$chr = factor(segs$chr, levels=c(1:22), ordered = T)

@@

#randNormal = paste(unlist(strsplit(randNormal, '_'))[c(1,3)], collapse='_')
#randBE = paste(unlist(strsplit(randBE, '_'))[c(1,3)], collapse='_')
```

@@

@@

p3 = ggplot(preds.normal, aes(Prob)) + geom_histogram(aes(fill=..x..), breaks=seq(0,1,0.1) , show.legend = F) +
  scale_fill_gradientn(colors = myPal,  name='') +
  labs(title='Predictions on BLD/Gastric', y='n Samples', x='Unadjusted Probability')

@@

table(subset(pred.qc, !lowsca)$Status)
table(subset(pred.qc, !lowsca)$Status)/table(pred.qc$Status)

ggplot(pred.qc, aes(`mean(SCA.Ratio)`))  + geom_histogram() + facet_wrap(~Status, scales='free_y')

ggplot(pred.qc, aes(`mean(Purity)`))  + geom_histogram() + facet_wrap(~Status, scales='free_y')

>>>>

load('~/Data/Ellie/Analysis/5e6_arms_all-NOQC/model_data.Rdata', verbose = T)
load('~/Data/Ellie/Analysis/5e6_arms_all-NOQC/all.pt.alpha.Rdata', verbose = T)
#alpha = '0'
alpha = '0.9'
fitV = models[[alpha]]
l = performance.at.1se[[alpha]]$lambda
features = coefs[[alpha]]

@@

```{r rnormals, echo=F, warning=F, message=F, fig.width=10, fig.height=8, eval=T}
randNormal = sample( grep('BLD',rownames(mergedSegs)[nm.rows], value=T), 1)
pt = unlist(strsplit(randNormal, '_'))[1]
segs = subset(segments.list[[pt]], chr %in% c(1:22) & grepl(sub('_', '.*', randNormal),sample))
segs$chr = factor(segs$chr, levels=c(1:22), ordered = T)

@@

#randNormal = paste(unlist(strsplit(randNormal, '_'))[c(1,3)], collapse='_')
#randBE = paste(unlist(strsplit(randBE, '_'))[c(1,3)], collapse='_')

@@

For blood normals only `r signif(nrow(subset(preds.normal, grepl('BLD',Samplename) & Prob < 0.5))/nrow(subset(preds.normal, grepl('BLD',Samplename) )),2)` have a <50% probabilitye (TPR).

@@

preds.normal = preds.normal %>% dplyr::mutate(Type = ifelse(grepl('BLD',Samplename), 'Blood','Gastric'))

p3 = ggplot(preds.normal, aes(Prob)) + facet_wrap(~Type, ncol=2, scales = 'free') +
  geom_histogram(aes(fill=..x..), breaks=seq(0,1,0.1) , show.legend = F) +
  scale_fill_gradientn(colors = myPal,  name='') +
  labs(title='Predictions on BLD/Gastric', y='n Samples', x='Unadjusted Probability')

@@

pander(
  rbind(rbind('n.Samples'=table(subset(pred.qc, !lowsca)$Status)),
  rbind('n.Patients'=table(unique(subset(pred.qc, !lowsca, select=c('PatientID','Status')))$Status))),
caption='Number of samples and patients that pass the low SCA:high purity thresholds')
